NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-08-16 paper/Chapters/Chapter3.tex
discussion updated

\begin{tabular}[t]{lcccc}
	\hiderowcolors
	\toprule
	\textbf{Variables} & \textbf{\Centerstack{Low carbo-\\hydrate eaters\\(n = 1730)}} & \textbf{\Centerstack{Moderate carbo-\\hydrate eaters\\(n = 1772)}} & \textbf{\Centerstack{High carbo-\\hydrate eaters\\(n = 2653)}} & \textbf{\textit{P} value} \textsuperscript{*}\\
	\midrule
	\showrowcolors
	Total (\%) & 28.4 (26.9, 29.9) & 28.7 (27.1, 30.3) & 43.0 (41.3, 44.7) & \\
	Country (\%) &  &  &  & 0.007\\
	\hspace{1em}England & 84.5 (81.7, 86.9) & 82.0 (79.3, 84.5) & 84.7 (82.3, 86.8) & \\
	\hspace{1em}Northern Ireland & 2.1 (1.6, 2.8) & 4.2 (3.2, 5.6) & 2.2 (1.7, 3.0) & \\
	\hspace{1em}Scotland & 9.1 (7.0, 11.8) & 8.6 (6.7, 11.1) & 8.0 (6.3, 10.2) & \\
	\hspace{1em}Wales & 4.3 (3.3, 5.6) & 5.1 (4.0, 6.4) & 5.1 (4.0, 6.4) & \\
	Age (years) & 51.0 (49.9, 52.1) & 40.3 (39.1, 41.6) & 51.7 (50.7, 52.7) & < 0.001\\
	Sex (\%) &  &  &  & 0.119\\
	\hspace{1em}Men & 50.0 (46.9, 53.1) & 50.2 (47.0, 53.5) & 46.6 (44.0, 49.1) & \\
	\hspace{1em}Women & 50.0 (46.9, 53.1) & 49.8 (46.5, 53.0) & 53.4 (50.9, 56.0) & \\
	Survey years (\% in rows) &  &  &  & 0.015\\
	\hspace{1em}1 & 32.5 (28.4, 36.9) & 26.3 (21.9, 31.2) & 41.2 (36.6, 46.0) & \\
	\hspace{1em}2 & 26.8 (22.6, 31.3) & 22.6 (18.6, 27.3) & 50.6 (45.8, 55.4) & \\
	\hspace{1em}3 & 22.6 (18.8, 26.9) & 33.7 (28.6, 39.2) & 43.6 (38.7, 48.7) & \\
	\hspace{1em}4 & 27.9 (24.1, 32.2) & 27.6 (23.8, 31.8) & 44.4 (40.2, 48.7) & \\
	\hspace{1em}5 & 27.9 (24.2, 32.0) & 28.7 (24.4, 33.5) & 43.3 (38.2, 48.6) & \\
	\hspace{1em}6 & 28.0 (24.0, 32.4) & 31.5 (26.9, 36.6) & 40.5 (35.8, 45.3) & \\
	\hspace{1em}7 & 29.1 (25.2, 33.4) & 29.0 (24.5, 34.0) & 41.8 (37.1, 46.7) & \\
	\hspace{1em}8 & 31.1 (27.3, 35.3) & 30.5 (25.9, 35.5) & 38.4 (34.1, 42.8) & \\
	Paid employment\textsuperscript{\dag} (\%) &  &  &  & 0.907\\
	\hspace{1em}Yes & 40.3 (37.0, 43.6) & 40.8 (37.1, 44.5) & 39.8 (37.1, 42.6) & \\
	\hspace{1em}No & 59.7 (56.4, 63.0) & 59.2 (55.5, 62.9) & 60.2 (57.4, 62.9) & \\
	Live with partner\textsuperscript{\ddag} (\%) &  &  &  & < 0.001\\
	\hspace{1em}Yes & 56.9 (53.6, 60.1) & 38.4 (35.2, 41.8) & 61.3 (58.7, 63.7) & \\
	\hspace{1em}No & 43.1 (39.9, 46.4) & 61.6 (58.2, 64.8)) & 38.7 (36.3, 41,3) & \\
	Household income, \textsterling/year & \Centerstack{36558.5\\(34800.2, 38316.8)} & \Centerstack{27180.8\\(25597.9, 28763.7)} & \Centerstack{32171.6\\(31024.9, 33318.2)} & < 0.001\\
	Ethnicity (\%) &  &  &  & \\
	\hspace{1em}White & 94.2 (92.4, 95.6) & 79.5 (76.4, 82.3) & 91.9 (90.1, 93.4) & < 0.001\\
	\hspace{1em}Non-White & 5.8 (4.4, 7.6) & 20.5 (17.7, 23.6) & 8.1 (6.6, 9.9) & \\
	Education (\%) &  &  &  & \\
	\hspace{1em}Degree or higher & 29.0 (26.1, 32.1) & 23.3 (20.5, 26.3) & 26.2 (24.1, 28.5) & 0.019\\
	\hspace{1em}Lower than degree & 71.0 (67.9, 73.9) & 76.7 (73.7, 79.5) & 73.8 (71.5, 75.9) & \\
	\bottomrule
	\multicolumn{5}{l}{{\scriptsize \textit{Note: }}}\\
	\multicolumn{5}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
	\multicolumn{5}{l}{{\scriptsize Variables were weighted by individual weights.}}\\
	\multicolumn{5}{l}{{\scriptsize \textsuperscript{*} For continuous variables, the \textit{F} test was used to determine differences between latent classes with Bonferroni}}\\ 
	\multicolumn{5}{l}{{\scriptsize correction to account for multiple testing across $>$ 2 classes. For categorical variables, differences between}}\\
	\multicolumn{5}{l}{{\scriptsize  latent classes were assessed using the adjusted Pearson $\chi^2$ test for survey data.}} \\
	\multicolumn{5}{l}{{\scriptsize \textsuperscript{\dag} Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey.} }\\
	\multicolumn{5}{l}{{\scriptsize \textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally recognised civil}} \\
	\multicolumn{5}{l}{{\scriptsize partnership.}}\\
\end{tabular}

@@

		\multicolumn{5}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;}}\\

@@

		\multicolumn{7}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference.}}\\

@@

	\caption{\label{tab:tab2HYT} ORs (95\%CI) of carbohydrate eating patterns with hypertension in the UK adults, with or without diabetes .\\ (NDNS RP 2008/09-15/16, sample size = 6155)}\vspace{-0.3cm}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{lccccc}
		\hiderowcolors
		\toprule
		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Carbohydrate eating patterns}} \\
		\cmidrule(l{2pt}r{2pt}){2-6}
		\textbf{Model} & \textbf{Low} & \textbf{Moderate} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{High} & \textbf{\textit{P} value\textsuperscript{*}}\\
		\midrule
		\showrowcolors
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Men (n = 2537)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension}}\\
		\hspace{1em}\hspace{1em}Crude model & 1 & 0.48 (0.33, 0.70) & < 0.001 & 0.82 (0.59, 1.13) & 0.217\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & 1 & 0.68 (0.43, 1.07) & 0.093 & 0.80 (0.56, 1.15) & 0.227\\
		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.64 (0.41, 1.01) & 0.054 & 0.75 (0.53, 1.08) & 0.124\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & 1 & 0.49 (0.33, 0.73) & < 0.001 & 0.82 (0.59, 1.14) & 0.241\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & 1 & 0.69 (0.43, 1.09) & 0.110 & 0.78 (0.54, 1.14) & 0.197\\
		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.65 (0.41, 1.03) & 0.066 & 0.73 (0.51, 1.06) & 0.096\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Women (n = 3618)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension}}\\
		\hspace{1em}\hspace{1em}Crude model & 1 & 0.52 (0.36, 0.75) & < 0.001 & 0.96 (0.72, 1.28) & 0.773\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\ddag} & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.89 (0.61, 1.30) & 0.552\\
		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.78 (0.45, 1.36) & 0.384 & 0.88 (0.62, 1.26) & 0.483\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & 1 & 0.51 (0.35, 0.74) & < 0.001 & 0.98 (0.73, 1.31) & 0.875\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\ddag} & 1 & 0.79 (0.44, 1.42) & 0.435 & 0.89 (0.61, 1.29) & 0.534\\
		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.87 (0.61, 1.25) & 0.452\\
		\bottomrule
		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: OR, odds ratio; CI, confidence interval; BMI, body mass index; WC, waist}}\\
		\multicolumn{6}{l}{{\scriptsize  circumference; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other}}\\
		\multicolumn{6}{l}{{\scriptsize covariates remained the same with the corresponding Model 1s.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from logistic regression models.}}\\ 
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age (continuous), live with partner or not (binary), education level}}\\ 
		\multicolumn{6}{l}{{\scriptsize (higher or equal to degree level or not), BMI, smoking status (current, ex-smoker, never)}}\\
		\multicolumn{6}{l}{{\scriptsize , total energy intake (kJ);}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, live with partner or not, average household income (continuous),}}\\ 
		\multicolumn{6}{l}{{\scriptsize education level, BMI, smoking status, total energy intake (kJ), alcohol consumption (g/day);}}\\
	\end{tabular}
\end{table}
\vspace{-0.5cm}
\rowcolors{2}{white}{white}

@@

\textbf{Table \ref{tab:tab2BMI}} shows the characteristics for participants according to their obesity status stratified by sex. The survey design-weighted prevalence for being overweight and obese in the UK adults were estimated to be 43.4\% and 25.7\% in men, and 30.9\% and 27.4\% in women. Obviously, abdominal obesity (WC) increased significantly with the elevated BMI level in both men and women. Overweight or obese participants were older, having lower total energy intake and lower carbohydrate intake compared with normal weight men and women (\textit{p} < 0.001). Moreover, edu-

@@

			\multicolumn{9}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference.}}\\

@@

	\caption{\label{tab:tab2BMI}Associations of carbohydrate eating patterns with BMI in the UK adults, with or without diabetes. \\ (NDNS RP 2008/09-15/16, sample size = 6155)}\vspace{-0.3cm}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{lccccc}
		\hiderowcolors
		\toprule
		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Carbohydrate eating patterns}} \\
		\cmidrule(l{2pt}r{2pt}){2-6}
		\textbf{Model} & \textbf{Low} & \textbf{Moderate} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{High} & \textbf{\textit{P} value\textsuperscript{*}}\\
		\midrule
		\showrowcolors
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Men (n = 2537)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.78 (-1.62, 0.06) & 0.068 & -0.28 (-0.96, 0.41) & 0.426\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.20 (-1.06, 0.66) & 0.654 & -0.43 (-1.13, 0.26) & 0.220\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.65 (-1.49, 0.19) & 0.127 & -0.21 (-0.89, 0.48) & 0.557\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.10 (-0.97, 0.77) & 0.820 & -0.39 (-1.10, 0.31) & 0.269\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Women (n = 3618)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.30 (-1.18, 0.57) & 0.496 & -0.76 (-1.44, -0.82) & 0.028\\
		\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & -0.93 (-2.33, 0.46) & 0.188 & -1.76 (-2.78, -0.73) & 0.001\\
		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 1.17 (-0.35, 2.70) & 0.132 & 0.57 (-0.58, 1.719 & 0.332\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.24 (-1.12, 0.65) & 0.601 & -0.71 (-1.39, -0.03) & 0.040\\
		\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & -0.86 (-2.28, 0.55) & 0.232 & -1.62 (-2.65, -0.58) & 0.002\\
		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 1.22 (-0.34, 2.78) & 0.124 & 0.43 (-0.71, 1.56) & 0.462\\
%		\bottomrule \\
    	\bottomrule
		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from linear regression models.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total }}\\
		\multicolumn{6}{l}{{\scriptsize  energy intake, alcohol consumption;}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, average household income, education level, hypertension, smoking status, total energy}}\\ 
		\multicolumn{6}{l}{{\scriptsize  intake, alcohol consumption.}}\\
	\end{tabular}
\end{table}

@@

%			\multicolumn{12}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; WC, waist circumference; NDNS RP, national dietary and nutrition survey rolling programme.}}\\

>>>>

\begin{tabular}[t]{lcccc}
	\hiderowcolors
	\toprule
	\textbf{Variables} & \textbf{\Centerstack{Low carbo-\\hydrate eaters\\(n = 1730)}} & \textbf{\Centerstack{Moderate carbo-\\hydrate eaters\\(n = 1772)}} & \textbf{\Centerstack{High carbo-\\hydrate eaters\\(n = 2653)}} & \textbf{\textit{P} value} \textsuperscript{*}\\
	\midrule
	\showrowcolors
	Total (\%) & 28.4 (26.9, 29.9) & 28.7 (27.1, 30.3) & 43.0 (41.3, 44.7) & \\
	Country (\%) &  &  &  & 0.007\\
	\hspace{1em}England & 84.5 (81.7, 86.9) & 82.0 (79.3, 84.5) & 84.7 (82.3, 86.8) & \\
	\hspace{1em}Northern Ireland & 2.1 (1.6, 2.8) & 4.2 (3.2, 5.6) & 2.2 (1.7, 3.0) & \\
	\hspace{1em}Scotland & 9.1 (7.0, 11.8) & 8.6 (6.7, 11.1) & 8.0 (6.3, 10.2) & \\
	\hspace{1em}Wales & 4.3 (3.3, 5.6) & 5.1 (4.0, 6.4) & 5.1 (4.0, 6.4) & \\
	Age (years) & 51.0 (49.9, 52.1) & 40.3 (39.1, 41.6) & 51.7 (50.7, 52.7) & < 0.001\\
	Sex (\%) &  &  &  & 0.119\\
	\hspace{1em}Men & 50.0 (46.9, 53.1) & 50.2 (47.0, 53.5) & 46.6 (44.0, 49.1) & \\
	\hspace{1em}Women & 50.0 (46.9, 53.1) & 49.8 (46.5, 53.0) & 53.4 (50.9, 56.0) & \\
	Survey years (\% in rows) &  &  &  & 0.015\\
	\hspace{1em}1 & 32.5 (28.4, 36.9) & 26.3 (21.9, 31.2) & 41.2 (36.6, 46.0) & \\
	\hspace{1em}2 & 26.8 (22.6, 31.3) & 22.6 (18.6, 27.3) & 50.6 (45.8, 55.4) & \\
	\hspace{1em}3 & 22.6 (18.8, 26.9) & 33.7 (28.6, 39.2) & 43.6 (38.7, 48.7) & \\
	\hspace{1em}4 & 27.9 (24.1, 32.2) & 27.6 (23.8, 31.8) & 44.4 (40.2, 48.7) & \\
	\hspace{1em}5 & 27.9 (24.2, 32.0) & 28.7 (24.4, 33.5) & 43.3 (38.2, 48.6) & \\
	\hspace{1em}6 & 28.0 (24.0, 32.4) & 31.5 (26.9, 36.6) & 40.5 (35.8, 45.3) & \\
	\hspace{1em}7 & 29.1 (25.2, 33.4) & 29.0 (24.5, 34.0) & 41.8 (37.1, 46.7) & \\
	\hspace{1em}8 & 31.1 (27.3, 35.3) & 30.5 (25.9, 35.5) & 38.4 (34.1, 42.8) & \\
	Paid employment\textsuperscript{\dag} (\%) &  &  &  & 0.907\\
	\hspace{1em}Yes & 40.3 (37.0, 43.6) & 40.8 (37.1, 44.5) & 39.8 (37.1, 42.6) & \\
	\hspace{1em}No & 59.7 (56.4, 63.0) & 59.2 (55.5, 62.9) & 60.2 (57.4, 62.9) & \\
	Live with partner\textsuperscript{\ddag} (\%) &  &  &  & < 0.001\\
	\hspace{1em}Yes & 56.9 (53.6, 60.1) & 38.4 (35.2, 41.8) & 61.3 (58.7, 63.7) & \\
	\hspace{1em}No & 43.1 (39.9, 46.4) & 61.6 (58.2, 64.8)) & 38.7 (36.3, 41,3) & \\
	Household income, \textsterling/year & \Centerstack{36558.5\\(34800.2, 38316.8)} & \Centerstack{27180.8\\(25597.9, 28763.7)} & \Centerstack{32171.6\\(31024.9, 33318.2)} & < 0.001\\
	Ethnicity (\%) &  &  &  & \\
	\hspace{1em}White & 94.2 (92.4, 95.6) & 79.5 (76.4, 82.3) & 91.9 (90.1, 93.4) & < 0.001\\
	\hspace{1em}Non-White & 5.8 (4.4, 7.6) & 20.5 (17.7, 23.6) & 8.1 (6.6, 9.9) & \\
	Education (\%) &  &  &  & \\
	\hspace{1em}Degree or higher & 29.0 (26.1, 32.1) & 23.3 (20.5, 26.3) & 26.2 (24.1, 28.5) & 0.019\\
	\hspace{1em}Lower than degree & 71.0 (67.9, 73.9) & 76.7 (73.7, 79.5) & 73.8 (71.5, 75.9) & \\
	\bottomrule
	\multicolumn{5}{l}{{\scriptsize \textit{Note: }}}\\
	\multicolumn{5}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national diet and nutrition survey rolling programme.}}\\
	\multicolumn{5}{l}{{\scriptsize Variables were weighted by individual weights.}}\\
	\multicolumn{5}{l}{{\scriptsize \textsuperscript{*} For continuous variables, the \textit{F} test was used to determine differences between latent classes with Bonferroni}}\\ 
	\multicolumn{5}{l}{{\scriptsize correction to account for multiple testing across $>$ 2 classes. For categorical variables, differences between}}\\
	\multicolumn{5}{l}{{\scriptsize  latent classes were assessed using the adjusted Pearson $\chi^2$ test for survey data.}} \\
	\multicolumn{5}{l}{{\scriptsize \textsuperscript{\dag} Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey.} }\\
	\multicolumn{5}{l}{{\scriptsize \textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally recognised civil}} \\
	\multicolumn{5}{l}{{\scriptsize partnership.}}\\
\end{tabular}

@@

		\multicolumn{5}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national diet and nutrition survey rolling programme;}}\\

@@

		\multicolumn{7}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national diet and nutrition survey rolling programme; BMI body mass index; WC, waist circumference.}}\\

@@

	\caption{\label{tab:tab2HYT} ORs (95\%CI) of carbohydrate eating patterns with hypertension in the UK adults, with or without diabetes .\\ (NDNS RP 2008/09-15/16, sample size = 6155)}\vspace{-0.3cm}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{lccccc}
		\hiderowcolors
		\toprule
		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Carbohydrate eating patterns}} \\
		\cmidrule(l{2pt}r{2pt}){2-6}
		\textbf{Model} & \textbf{Low} & \textbf{Moderate} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{High} & \textbf{\textit{P} value\textsuperscript{*}}\\
		\midrule
		\showrowcolors
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Men (n = 2537)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension}}\\
		\hspace{1em}\hspace{1em}Crude model & 1 & 0.48 (0.33, 0.70) & < 0.001 & 0.82 (0.59, 1.13) & 0.217\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & 1 & 0.68 (0.43, 1.07) & 0.093 & 0.80 (0.56, 1.15) & 0.227\\
		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.64 (0.41, 1.01) & 0.054 & 0.75 (0.53, 1.08) & 0.124\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & 1 & 0.49 (0.33, 0.73) & < 0.001 & 0.82 (0.59, 1.14) & 0.241\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & 1 & 0.69 (0.43, 1.09) & 0.110 & 0.78 (0.54, 1.14) & 0.197\\
		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.65 (0.41, 1.03) & 0.066 & 0.73 (0.51, 1.06) & 0.096\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Women (n = 3618)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension}}\\
		\hspace{1em}\hspace{1em}Crude model & 1 & 0.52 (0.36, 0.75) & < 0.001 & 0.96 (0.72, 1.28) & 0.773\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\ddag} & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.89 (0.61, 1.30) & 0.552\\
		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.78 (0.45, 1.36) & 0.384 & 0.88 (0.62, 1.26) & 0.483\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & 1 & 0.51 (0.35, 0.74) & < 0.001 & 0.98 (0.73, 1.31) & 0.875\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\ddag} & 1 & 0.79 (0.44, 1.42) & 0.435 & 0.89 (0.61, 1.29) & 0.534\\
		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.87 (0.61, 1.25) & 0.452\\
		\bottomrule
		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: OR, odds ratio; CI, confidence interval; BMI, body mass index; WC, waist}}\\
		\multicolumn{6}{l}{{\scriptsize  circumference; NDNS RP, national diet and nutrition survey rolling programme.}}\\
		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other}}\\
		\multicolumn{6}{l}{{\scriptsize covariates remained the same with the corresponding Model 1s.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from logistic regression models.}}\\ 
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age (continuous), live with partner or not (binary), education level}}\\ 
		\multicolumn{6}{l}{{\scriptsize (higher or equal to degree level or not), BMI, smoking status (current, ex-smoker, never)}}\\
		\multicolumn{6}{l}{{\scriptsize , total energy intake (kJ);}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, live with partner or not, average household income (continuous),}}\\ 
		\multicolumn{6}{l}{{\scriptsize education level, BMI, smoking status, total energy intake (kJ), alcohol consumption (g/day);}}\\
	\end{tabular}
\end{table}
\vspace{-0.5cm}
\rowcolors{2}{white}{white}

@@

\textbf{Table \ref{tab:tab1BMI}} shows the characteristics for participants according to their obesity status stratified by sex. The survey design-weighted prevalence for being overweight and obese in the UK adults were estimated to be 43.4\% and 25.7\% in men, and 30.9\% and 27.4\% in women. Obviously, abdominal obesity (WC) increased significantly with the elevated BMI level in both men and women. Overweight or obese participants were older, having lower total energy intake and lower carbohydrate intake compared with normal weight men and women (\textit{p} < 0.001). Moreover, edu-

@@

			\multicolumn{9}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national diet and nutrition survey rolling programme; BMI body mass index; WC, waist circumference.}}\\

@@

	\caption{\label{tab:tab2BMI}Associations of carbohydrate eating patterns with BMI in the UK adults, with or without diabetes. \\ (NDNS RP 2008/09-15/16, sample size = 6155)}\vspace{-0.3cm}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{lccccc}
		\hiderowcolors
		\toprule
		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Carbohydrate eating patterns}} \\
		\cmidrule(l{2pt}r{2pt}){2-6}
		\textbf{Model} & \textbf{Low} & \textbf{Moderate} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{High} & \textbf{\textit{P} value\textsuperscript{*}}\\
		\midrule
		\showrowcolors
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Men (n = 2537)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.78 (-1.62, 0.06) & 0.068 & -0.28 (-0.96, 0.41) & 0.426\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.20 (-1.06, 0.66) & 0.654 & -0.43 (-1.13, 0.26) & 0.220\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.65 (-1.49, 0.19) & 0.127 & -0.21 (-0.89, 0.48) & 0.557\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.10 (-0.97, 0.77) & 0.820 & -0.39 (-1.10, 0.31) & 0.269\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Women (n = 3618)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.30 (-1.18, 0.57) & 0.496 & -0.76 (-1.44, -0.82) & 0.028\\
		\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & -0.93 (-2.33, 0.46) & 0.188 & -1.76 (-2.78, -0.73) & 0.001\\
		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 1.17 (-0.35, 2.70) & 0.132 & 0.57 (-0.58, 1.719 & 0.332\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.24 (-1.12, 0.65) & 0.601 & -0.71 (-1.39, -0.03) & 0.040\\
		\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & -0.86 (-2.28, 0.55) & 0.232 & -1.62 (-2.65, -0.58) & 0.002\\
		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 1.22 (-0.34, 2.78) & 0.124 & 0.43 (-0.71, 1.56) & 0.462\\
%		\bottomrule \\
    	\bottomrule
		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; NDNS RP, national diet and nutrition survey rolling programme.}}\\
		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from linear regression models.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total }}\\
		\multicolumn{6}{l}{{\scriptsize  energy intake, alcohol consumption;}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, average household income, education level, hypertension, smoking status, total energy}}\\ 
		\multicolumn{6}{l}{{\scriptsize  intake, alcohol consumption.}}\\
	\end{tabular}
\end{table}

@@

%			\multicolumn{12}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; WC, waist circumference; NDNS RP, national diet and nutrition survey rolling programme.}}\\
